\section{Threat Model}
Assuming that the Naigama parser, like many parsers, implements the
following workflow sequence:

\begin{itemize}
\item A policy that comprehensively describes the structure
      of a piece of input data is written down in a grammar.
\item The grammar is held against
      a piece of real input data by an engine (via, in this case,
      a process of compilation and assembly to a bytecode).
\item The engine provides a conclusion: the real
      input data either matches the grammar or it doesn't.
\item Optional detail of matching inputs follow, or subsequent actions
      are performed on the input.
\end{itemize}

This paper then proposes that a parser is threatened by the following phenomena
(apart from malicious inputs, or inputs which have been changed before being
offered to the engine, which are considered
an elementary form of protection that a parser should offer):

\refstepcounter{defctr}
\newcounter{threatintent} \setcounter{threatintent}{\value{defctr}}
\thedefctr .
The intention of the grammar writer is not easily conveyed in bytecode
(and is therefore prone to mistakes).

The intention of the grammar writer is not correctly conveyed in
bytecode, and:

\refstepcounter{defctr}
\newcounter{threatbcerror} \setcounter{threatbcerror}{\value{defctr}}
\thedefctr .
This is something that can be proven before execution.

\refstepcounter{defctr}
\newcounter{threatbcexec} \setcounter{threatbcexec}{\value{defctr}}
\thedefctr .
This only becomes apparent during execution.

The intention of the grammar writer is correctly conveyed in bytecode,
but the bytecode is somehow corrupted, because either:

\refstepcounter{defctr}
\newcounter{threatbcsign} \setcounter{threatbcsign}{\value{defctr}}
\thedefctr .
The bytecode is replaced by a malicious or stupid actor before execution, or

\refstepcounter{defctr}
\newcounter{threatbcupset} \setcounter{threatbcupset}{\value{defctr}}
\thedefctr .
Some of the bytecode's bits accidentally change value before or
during execution.

\refstepcounter{defctr}
\newcounter{threatengine} \setcounter{threatengine}{\value{defctr}}
\thedefctr .
The intention of the grammar writer is correctly conveyed in bytecode,
but the engine is somehow corrupted during execution.

\refstepcounter{defctr}
\newcounter{threatinput} \setcounter{threatinput}{\value{defctr}}
\thedefctr .
The input is somehow corrupted during execution.
